---
editor: source
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
source(here::here("site", "common.R"))
```

## Measures {#sec-measures}

The following table provides a brief overview of the measures used in this benchmark.
Unfortunately, during early benchmark development slightly different shorthand names were used for the measures in filenames for result files than the abbreviations used in the paper.

- `id` refers to the shorthand used in the result files listed above.
- `mlr_id` refers to the measure as it is implemented in [mlr3proba](https://mlr3proba.mlr-org.com/reference/index.html#survival-measures)
- `Label` refers to the measure as it is named consistently throughout the paper and resulting plots.

| id                   | mlr3 id            | Label                                                        |
|:---------------------|:-------------------|:-------------------------------------------------------------|
| `harrell_c`          | `surv.cindex`      | Harrell's C                                                  |
| `uno_c`              | `surv.cindex`      | Uno's C                                                      |
| `rcll`               | `surv.rcll`        | Right-Censored Log Loss (RCLL)                               |
| `rcll_erv`           | `surv.rcll`        | Right-Censored Log Loss (RCLL) [ERV]                         |
| `intlogloss`         | `surv.intlogloss`  | Re-weighted Integrated Survival Log-Likelihood (RISLL)       |
| `intlogloss_erv`     | `surv.intlogloss`  | Re-weighted Integrated Survival Log-Likelihood (RISLL) [ERV] |
| `logloss`            | `surv.logloss`     | Re-weighted Negative Log-Likelihood (RNLL)                   |
| `logloss_erv`        | `surv.logloss`     | Re-weighted Negative Log-Likelihood (RNLL) [ERV]             |
| `brier_improper`     | `surv.brier`       | Integrated Survival Brier Score (ISBS)                       |
| `brier_improper_erv` | `surv.brier`       | Integrated Survival Brier Score (ISBS) [ERV]                 |
| `dcalib`             | `surv.dcalib`      | D-Calibration                                                |
| `caliba_ratio`       | `surv.calib_alpha` | Van Houwelingen's Alpha                                      |


## Tasks {#sec-tasks}

The following table gives a summary of the included datasets (tasks) in the benchmark.

```{r task-tab}
# tasks = load_task_data()
tasktab = load_tasktab()

tasktab |>
  dplyr::select(task_id, n, p, events, censprop, n_uniq_t) |>
  dplyr::arrange(-n) |>
  dplyr::mutate(
    n = n,
    p = p,
    events = events,
    censprop = round(100 * censprop, 1),
    n_uniq_t = n_uniq_t
  ) |>
  setNames(c("Dataset", "N", "p", "Events", "Censoring %", "# Unique Time Points")) |>
  reactable::reactable(sortable = TRUE, filterable = TRUE, pagination = FALSE)
```

## Learners {#sec-learners}

This table shows the models (learners) used in the benchmark with their `mlr3` IDs and additional metadata.

- "Parameters" is 0 for learners such as KM, NA, CPH, which do not have any hyperparameters. It is also 0 for CoxBoost, which uses its own tuning method.
- "Internal CV" indicates learners internally perform CV, e.g., glmnet, CoxBoost.
- "Encode" indicates whether treatment encoding is performed as part of the pre-processing pipeline **before** the learner sees the data.
- "Scale" analogously indicates whether scaling to unit variance and 0 mean is performed.
- "Grid Search" indicates whether the tuning space was small enough to perform exhaustive grid search with fewer than 50 evaluations

```{r learner-tab}
lrntbab = load_lrntab()

lrntab |>
  dplyr::mutate(dplyr::across(dplyr::where(is.logical), \(x) ifelse(x, "\u2705", ""))) |>
  kableExtra::kbl(
    align = "llccccc",
    col.names = c("Learner", "mlr3 ID", "Parameters", "Internal CV", "Encode", "Scale", "Grid Search")
  ) |>
  kableExtra::kable_styling() |>
  kableExtra::column_spec(2, width = "5%") |>
  kableExtra::column_spec(3, width = "5%") |>
  kableExtra::column_spec(4, width = "20%") |>
  kableExtra::column_spec(7, width = "25%") 
``` 

