---
editor: source
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
source(here::here("common.R"))
```

In the mlr3 ecosystem it is more common to refer to _tasks_ and _learners_ rather than _datasets_ and _models_, and there are real differences between the terms which we unfortunately use inconsistently.

## Measures {#sec-measures}

The following table provides a brief overview of the measures used in this benchmark.
Unfortunately, the identifiers used under the hood do not directly correspond to measure names and abbreviations as used in the paper.

- `ID` refers to the shorthand used in the result files listed above.
- `mlr3 ID` refers to the measure as it is implemented in [mlr3proba](https://mlr3proba.mlr-org.com/reference/index.html#survival-measures)
- `Label` refers to the measure as it is named consistently throughout the paper and resulting plots.

```{r measures-tab}
msr_tbl |>
  dplyr::select(type, id, mlr_id, label) |>
  knitr::kable(col.names = c("Type", "ID", "mlr3 ID", "Label")) |>
  kableExtra::kable_styling() |>
  kableExtra::column_spec(2:3, monospace = TRUE) |>
  kableExtra::collapse_rows(1)
```

Integrated measures are always integrated up to the conventional 80% quantile.

## Tasks (Datasets) {#sec-tasks}

The following table gives a summary of the included tasks (datasets) in the benchmark.

Violation of the proportional hazards (PH) assumption is derived from the p-value of the global significance test conducted with `cox.zph()` at the 5% level (i.e., `ph_violated = p.value > 0.05`).

```{r task-tab}
tasktab |>
  dplyr::arrange(-n) |>
  dplyr::mutate(
    censprop = round(100 * censprop, 1),
    repeats = assign_repeats(events),
    ph_violated = factor(ifelse(ph_violated == 1, "Yes", "No")),
    noverp = round(noverp, 2)
  ) |>
  dplyr::select(task_id, repeats, n, p, noverp, events, censprop, n_uniq_t, ph_violated) |>
  setNames(c(
    "Dataset",
    "# CV Repeats",
    "N",
    "p",
    "n/p",
    "Events",
    "Censoring %",
    "# Unique Time Points",
    "PH violated"
  )) |>
  reactable::reactable(
    sortable = TRUE,
    filterable = TRUE,
    pagination = FALSE,
    columns = list(Dataset = reactable::colDef(minWidth = 150))
  )
```

## Learners (Models) {#sec-learners}

This table shows the learner (models) used in the benchmark with their `mlr3` IDs and additional metadata.

- "Parameters" is 0 for learners such as KM, NA, CPH, which do not have any hyperparameters. It is also 0 for CoxBoost, which uses its own tuning method.
- "Survival Prediction" indicates whether the learner provides a survival probability prediction (a `distr` object), which allows evaluation with measures like the ISBS.
- "Internal CV" indicates learners internally perform CV, i.e., GLMN (via `cv.glmnet`) and CoxB (via `optimCoxBoostPenalty()`).
- "Exhaustive Search" indicates whether the tuning space was small enough to perform exhaustive grid search with fewer than 50 evaluations
- "Scale" analogously indicates whether scaling to unit variance and 0 mean is performed.
- "Encode" indicates whether treatment encoding is performed as part of the pre-processing pipeline **before** the learner sees the data.

```{r learner-tab}
lrntab |>
  dplyr::select(id, base_lrn, surv_pred, params, internal_cv, grid, scale, encode) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.logical), \(x) ifelse(x, "\u2705", "---"))) |>
  kableExtra::kbl(
    align = "llccccc",
    caption = "Learner IDs in benchmark with associated mlr3 identifiers",
    col.names = c(
      "Learner",
      "mlr3 ID",
      "Survival Prediction",
      "Parameters",
      "Internal CV",
      "Exhaustive Search",
      "Scale",
      "Encode"
    )
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra::column_spec(2, width = "5%") |>
  kableExtra::column_spec(3, width = "5%")
# kableExtra::column_spec(4, width = "20%") |>
# kableExtra::column_spec(7, width = "25%")
``` 
