---
format:
  html:
    page-layout: full
    tbl-cap-location: top
editor: source
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
source(here::here("common.R"))
```

This page presents aggregated benchmark results, including statistical tests and critical difference plots.
Results are divided by tuning measure: `harrell_c` (discrimination) and `isbs` (proper scoring rule).

## Aggregated Results

Averaged scores across outer resampling folds for each task and learner.

### Discrimination

::: {.panel-tabset}

#### Boxplots

```{r aggr-boxplot-harrell-c}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Discrimination" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores,
    type = "box",
    eval_measure_id = measure_id,
    tuning_measure_id = "harrell_c",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Violin plots

```{r aggr-violin-harrell-c}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Discrimination" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "harrell_c",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Violin (no baselines)

```{r aggr-violin-harrell-c-no-outliers}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Discrimination" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("AK", "KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "harrell_c",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Scaled (Boxplots)

```{r aggr-boxplot-harrell-c-scaled}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Discrimination" & !erv, id]) {
  print(
    plot_aggr_scores(
      aggr_scores_scaled,
      type = "box",
      eval_measure_id = measure_id,
      tuning_measure_id = "harrell_c",
      dodge = FALSE,
      flip = TRUE
    ) %+%
      labs(
        title = glue::glue("{msr_tbl[id == measure_id, label]} [Scaled]"),
        subtitle = "Boxplot of aggregated scores across all tasks\nScaled such that 0 = KM, 1 = Best model"
      )
  )
}
```

#### Scaled (Violin)

```{r aggr-violin-harrell-c-scaled}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Discrimination" & !erv, id]) {
  print(
    plot_aggr_scores(
      aggr_scores_scaled[!(learner_id %in% c("KM", "NEL"))],
      type = "violin",
      eval_measure_id = measure_id,
      tuning_measure_id = "harrell_c",
      dodge = FALSE,
      flip = TRUE
    ) %+%
      labs(
        title = glue::glue("{msr_tbl[id == measure_id, label]} [Scaled]"),
        subtitle = "Violin plot of aggregated scores across all tasks\nScaled such that 0 = KM, 1 = Best model"
      )
  )
}
```

:::

### Overall Performance (ISBS)

::: {.panel-tabset}

#### Boxplots

```{r aggr-boxplot-isbs}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores,
    type = "box",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Violin plots

```{r aggr-violin-isbs}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Boxplots (no outliers)

```{r aggr-boxplot-isbs-no-outliers}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("AK", "NCV"))],
    type = "box",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Violin (no outliers + baselines)

```{r aggr-violin-isbs-no-outliers}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("AK", "NCV", "KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### ERV (Boxplots)

```{r aggr-boxplot-isbs-erv}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & erv, id]) {
  print(plot_aggr_scores(
    aggr_scores,
    type = "box",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### ERV (Violin)

```{r aggr-violin-isbs-erv}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### ERV Boxplots (no outliers)

```{r aggr-boxplot-isbs-erv-no-outliers}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("AK", "NCV"))],
    type = "box",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### ERV Violin (no outliers)

```{r aggr-violin-isbs-erv-no-outliers}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & erv, id]) {
  print(plot_aggr_scores(
    aggr_scores[!(learner_id %in% c("AK", "NCV", "KM", "NEL"))],
    type = "violin",
    eval_measure_id = measure_id,
    tuning_measure_id = "isbs",
    dodge = FALSE,
    flip = TRUE
  ))
}
```

#### Scaled (Boxplots)

```{r aggr-boxplot-isbs-scaled}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(
    plot_aggr_scores(
      aggr_scores_scaled,
      type = "box",
      eval_measure_id = measure_id,
      tuning_measure_id = "isbs",
      dodge = FALSE,
      flip = TRUE
    ) %+%
      labs(
        title = glue::glue("{msr_tbl[id == measure_id, label]} [Scaled]"),
        subtitle = "Boxplot of aggregated scores across all tasks\nScaled such that 0 = KM, 1 = Best model"
      )
  )
}
```

#### Scaled (Violin)

```{r aggr-violin-isbs-scaled}
#| fig-width: 11
#| fig-height: 8

for (measure_id in msr_tbl[type == "Scoring Rule" & !erv, id]) {
  print(
    plot_aggr_scores(
      aggr_scores_scaled[!(learner_id %in% c("KM", "NEL"))],
      type = "violin",
      eval_measure_id = measure_id,
      tuning_measure_id = "isbs",
      dodge = FALSE,
      flip = TRUE
    ) %+%
      labs(
        title = glue::glue("{msr_tbl[id == measure_id, label]} [Scaled]"),
        subtitle = "Violin plot of aggregated scores across all tasks\nScaled such that 0 = KM, 1 = Best model"
      )
  )
}
```

:::

### Calibration

#### D-Calibration

Calculating p-values for D-Calibration as `pchisq(score, 10 - 1, lower.tail = FALSE)`.

This represents more of a heuristic approach as an insignificant result implies a well-calibrated model, but a significant result does not necessarily imply a poorly calibrated model.
Furthermore, there is no multiplicity correction applied due to the generally exploratory nature of the plots.

```{r calibration-dcalib-heatmap, fig.width=10, fig.height=8}

aggr_scores |>
  dplyr::filter(grepl("isbs", tune_measure)) |>
  dplyr::mutate(
    dcalib_p = pchisq(dcalib, 10 - 1, lower.tail = FALSE),
    dcalib_label = fifelse(dcalib_p < 0.05, "X", "")
  ) |>
  ggplot(aes(
    x = forcats::fct_reorder(learner_id, dcalib_p),
    y = forcats::fct_rev(task_id),
    fill = dcalib_p
  )) +
  geom_tile(color = "#EEEEEE") +
  geom_text(aes(label = dcalib_label), color = "white", size = 3) +
  scale_fill_viridis_c(breaks = seq(0, 1, .1)) +
  guides(
    x = guide_axis(n.dodge = 2),
    fill = guide_colorbar(
      title.vjust = .8,
      barwidth = unit(200, "pt")
    )
  ) +
  labs(
    title = "D-Calibration p-values by task and learner",
    subtitle = glue::glue(
      "Models tuned on {msr_tbl[id == 'isbs', label]}\n",
      "Learners ordered by average p-value. X denotes p < 0.05"
    ),
    y = "Task",
    x = "Learner",
    color = NULL,
    fill = "p-value"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title.position = "plot",
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.spacing.x = unit(5, "mm"),
    panel.background = element_rect(fill = "#EEEEEE", color = "#EEEEEE")
  )


```

#### Alpha-Calibration

For this measure, calibration is indicated by a score close to 1. The red vertical line marks perfect calibration (alpha = 1).

```{r calibration-alpha-ratio}
#| fig-width: 7
#| fig-height: 8.5

aggr_scores |>
  dplyr::filter(grepl("isbs", tune_measure)) |>
  dplyr::filter(!(learner_id %in% c("AK", "NCV"))) |>
  ggplot(aes(x = alpha_calib)) +
  facet_wrap(vars(learner_id), scales = "free_y", ncol = 2) +
  geom_histogram(alpha = 1 / 4, color = "gray", fill = "darkgray") +
  geom_density(aes(y = after_stat(density)), color = "black") +
  geom_vline(xintercept = 1, color = "darkred") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(
    title = glue::glue("Alpha-Calibration scores across tasks (tuned on ISBS)"),
    y = "Count",
    x = "Alpha"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    plot.title.position = "plot",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = rel(0.75))
  )
```

### Raw scores

| Column              | Type  | Description |
| --------------------|-------|-------------|
| Group               | `fct` | Model / learner group, one of "Baseline", "Classical", "Trees", "Boosting" |
| Learner             | `fct` | Model / learner name, e.g. `RAN` for `ranger` |
| Task                | `fct` | Dataset name, e.g. `veteran`                  |
| Tuning              | `chr` | Tuning measure, one of `harrell_c`, `isbs`, or `harrell_c,isbs` for untuned learners or "self-tuners" |
| `harrell_c`, `uno_c`, `isll`, `isll_erv`, `isbs`, `isbs_erv`, `dcalib`, `alpha_calib` | `dbl` | Evaluation measure score |
| warn                | `int` | Number of warnings encountered during outer resampling |
| err                 | `int` | Number of errors encountered during outer resampling. Errors indicate failure and the prediction of KM was inserted as fallback |


```{r aggr-reactable}
#| column: page
library(reactable)
aggr_scores |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), \(x) round(x, 3))) |>
  dplyr::mutate(task_id = factor(task_id), tune_measure = factor(tune_measure)) |>
  dplyr::arrange(task_id, learner_id) |>
  dplyr::select(
    learner_group,
    learner_id,
    task_id,
    tune_measure,
    harrell_c:alpha_calib,
    warn = warnings_cnt,
    err = errors_cnt
  ) |>
  reactable::reactable(
    sortable = TRUE,
    filterable = TRUE,
    searchable = TRUE,
    defaultPageSize = 30,
    compact = TRUE,
    columns = list(
      learner_group = reactable::colDef(name = "Group", minWidth = 80),
      learner_id = reactable::colDef(name = "Learner", minWidth = 60),
      task_id = reactable::colDef(name = "Task", minWidth = 100),
      tune_measure = reactable::colDef(name = "Tuning", minWidth = 80),
      alpha_calib = reactable::colDef(name = "alpha calib", minWidth = 55),
      warn = reactable::colDef(name = "Warn", minWidth = 55),
      err = reactable::colDef(name = "Err", minWidth = 55)
    ),
    defaultColDef = reactable::colDef(minWidth = 70)
  )
```

## Statistical Analysis

### Global Friedman Test

::: {.panel-tabset}

#### Harrell's C


```{r friedman-harrell-c}
bma_harrell_c$friedman_test(p.adjust.method = "holm") |>
  tablify()
```

#### ISBS

```{r friedman-isbs}
bma_isbs$friedman_test(p.adjust.method = "holm") |>
  tablify()
```

:::

### Critical Difference Plots: Bonferroni-Dunn

Using Cox (`CPH`) as baseline for comparison, these represent the primary result of the benchmark.

::: {.panel-tabset}

#### Harrell's C

```{r critical-difference-baseline-diff-harrell-c-harrell-c}
#| fig-width: 10
#| fig-height: 6.25

cd_ratio = 10 / 11

plot_bma(
  bma = bma_harrell_c,
  type = "cd_bd",
  measure_id = "harrell_c",
  tuning_measure_id = "harrell_c",
  ratio = cd_ratio,
  baseline = "CPH"
)
```

#### ISBS

```{r critical-difference-baseline-diff-isbs-isbs}
#| fig-width: 10
plot_bma(
  bma = bma_isbs,
  type = "cd_bd",
  measure_id = "isbs",
  tuning_measure_id = "isbs",
  ratio = cd_ratio,
  baseline = "CPH"
)
```

:::
