---
format:
  html:
    page-layout: full
    tbl-cap-location: top
editor: source
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
source(here::here("common.R"))
source(here::here("../", "R", "plackettluce.R"))
library(PlackettLuce)
set.seed(2026)

scores_all = readRDS(fs::path(result_path, "scores.rds"))
exclude = c("KM", "NEL")
all_learners = function(measure) {
  setdiff(unique(scores_all[grepl(pattern = measure, tune_measure), learner_id]), exclude)
}
```

Plackett-Luce (PL) models are used as a sensitivity analysis complementary to the critical difference plots.
Each dataset acts as a "rater" providing a complete ranking over all models ("items").
KM and NEL baselines are excluded as they are uninformative for model comparison.

## Full Model

::: {.panel-tabset}

### Harrell's C

```{r pl-full-hc}
#| fig-width: 10
#| fig-height: 7

pl_full_hc = run_pl_ranking(scores_all, "harrell_c", minimize = FALSE, exclude, plot_path = NULL, msr_tbl = msr_tbl)
pl_full_hc$p
```

### ISBS

```{r pl-full-isbs}
#| fig-width: 10
#| fig-height: 7

pl_full_isbs = run_pl_ranking(scores_all, "isbs", minimize = TRUE, exclude, plot_path = NULL, msr_tbl = msr_tbl)
pl_full_isbs$p
```

:::

## Subgroup Analysis

Separate PL models are fit for subgroups based on dataset characteristics.
Likelihood ratio tests compare the combined log-likelihood of subgroup-specific models against the full model.

### PH Assumption Violation

::: {.panel-tabset}

#### Harrell's C

```{r pl-ph-hc}
#| fig-width: 12
#| fig-height: 7

pl_ph_hc = run_pl_ph_subgroups(scores_all, "harrell_c", minimize = FALSE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_ph_hc$p
```

```{r pl-ph-hc-lr}
lr_ph_hc = pl_lr_test(pl_full_hc$pl_fit, pl_ph_hc)
```

LR test p-value: `r format.pval(lr_ph_hc$p_value)`

#### ISBS

```{r pl-ph-isbs}
#| fig-width: 12
#| fig-height: 7

pl_ph_isbs = run_pl_ph_subgroups(scores_all, "isbs", minimize = TRUE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_ph_isbs$p
```

```{r pl-ph-isbs-lr}
lr_ph_isbs = pl_lr_test(pl_full_isbs$pl_fit, pl_ph_isbs)
```

LR test p-value: `r format.pval(lr_ph_isbs$p_value)`

:::

### Censoring Proportion

::: {.panel-tabset}

#### Harrell's C

```{r pl-cens-hc}
#| fig-width: 12
#| fig-height: 7

pl_cens_hc = run_pl_censprop_subgroups(scores_all, "harrell_c", minimize = FALSE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_cens_hc$p
```

```{r pl-cens-hc-lr}
lr_cens_hc = pl_lr_test(pl_full_hc$pl_fit, pl_cens_hc)
```

LR test p-value: `r format.pval(lr_cens_hc$p_value)`

#### ISBS

```{r pl-cens-isbs}
#| fig-width: 12
#| fig-height: 7

pl_cens_isbs = run_pl_censprop_subgroups(scores_all, "isbs", minimize = TRUE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_cens_isbs$p
```

```{r pl-cens-isbs-lr}
lr_cens_isbs = pl_lr_test(pl_full_isbs$pl_fit, pl_cens_isbs)
```

LR test p-value: `r format.pval(lr_cens_isbs$p_value)`

:::

### Sample Size to Feature Ratio (n/p)

::: {.panel-tabset}

#### Harrell's C

```{r pl-noverp-hc}
#| fig-width: 12
#| fig-height: 7

pl_noverp_hc = run_pl_noverp_subgroups(scores_all, "harrell_c", minimize = FALSE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_noverp_hc$p
```

```{r pl-noverp-hc-lr}
lr_noverp_hc = pl_lr_test(pl_full_hc$pl_fit, pl_noverp_hc)
```

LR test p-value: `r format.pval(lr_noverp_hc$p_value)`

#### ISBS

```{r pl-noverp-isbs}
#| fig-width: 12
#| fig-height: 7

pl_noverp_isbs = run_pl_noverp_subgroups(scores_all, "isbs", minimize = TRUE, exclude, tasktab, plot_path = NULL, msr_tbl = msr_tbl)
pl_noverp_isbs$p
```

```{r pl-noverp-isbs-lr}
lr_noverp_isbs = pl_lr_test(pl_full_isbs$pl_fit, pl_noverp_isbs)
```

LR test p-value: `r format.pval(lr_noverp_isbs$p_value)`

:::

## PL Trees

PL trees use model-based recursive partitioning to automatically detect dataset subgroups where model rankings differ significantly.

::: {.panel-tabset}

### Harrell's C (lenient)

```{r pltree-lenient-hc}
#| fig-width: 14
#| fig-height: 8

run_pl_tree(
  scores_all, "harrell_c", minimize = FALSE,
  learners = all_learners("harrell_c"), tasktab = tasktab,
  plot_name = "lenient", plot_path = NULL,
  alpha = 0.2, minsize = 5, bonferroni = TRUE, msr_tbl = msr_tbl
)$p
```

### ISBS (strict)

```{r pltree-strict-isbs}
#| fig-width: 14
#| fig-height: 8

run_pl_tree(
  scores_all, "isbs", minimize = TRUE,
  learners = all_learners("isbs"), tasktab = tasktab,
  plot_name = "strict", plot_path = NULL,
  alpha = 0.1, minsize = 10, bonferroni = TRUE, msr_tbl = msr_tbl
)$p
```

### ISBS (lenient)

```{r pltree-lenient-isbs}
#| fig-width: 14
#| fig-height: 8

run_pl_tree(
  scores_all, "isbs", minimize = TRUE,
  learners = all_learners("isbs"), tasktab = tasktab,
  plot_name = "lenient", plot_path = NULL,
  alpha = 0.2, minsize = 5, bonferroni = TRUE, msr_tbl = msr_tbl
)$p
```

:::
